\section{Proposed research}
The proposed research seeks to be able to compute the optimized position
and intensity of the photon beams as fast as possible. To do that, we need to
develop on three different topics :
\begin{itemize}
\item massive parallelization
\item efficient and fast algorithms to solve the transport problem
\item optimization of the intensity of the beams 
\end{itemize}

\subsection{Massive parallelization}
Parallelization is an important way to decrease the time needed to solve the
transport and the optimization problem. To do this, we will use
the capabilities of the Parallel Deterministic Transport code developed at
Texas A\&M University. 

\subsection{Efficient and fast algorithms}
This section consists in mainly three parts. The first one is the energy
discretization. We plan to use linear discontinuous finite element for the
energy discretization. This discretization scheme has shown good behavior
(less oscillations than the diamond difference scheme) for the self-adjoint
angular flux form of the equation (\ref{b-csd}) \cite{saaf} and the 
Boltzmann-Fokker-Planck equation \cite{fem}.\\
We need to define : 
\begin{align}
& \Delta E^g = E^{g-1/2} -E^{g+1/2}\\
& E^g = \frac{E^{g-1/2}+E^{g+1/2}}{2}\\
& \Psi^g(\br) = \int_{\Delta E^g} dE \Psi(\br,E)\\
& \Psi(\br,E) = \Psi^{g,T}\cdot b^g \ \ \forall E \in \[E^{g+1/2},E^{g-1/2}\]\\
& \Psi^g =
\begin{pmatrix}
\Psi_x^g\\
\Psi_E^g
\end{pmatrix}
\ \ \forall E \in \[E^{g+1/2},E^{g-1/2}\]\\
& b^g = 
\begin{pmatrix}
b_{\br}^g(\br,E)\\
b_E^g(E)
\end{pmatrix}
\ \ \forall E \in \[E^{g+1/2},E^{g-1/2}\]\\
& b_{\br}^g\(x,E\) = \frac{b_{\br}(\br)}{\Delta E^g}\ \ \forall \in
\[E^{g+1/2},E^{g-1/2}\]\\
& b_{\br} \textrm{ are discontinuous finite element basis functions}\\
& b_E^g\(E\) = \frac{2}{\(\Delta E^g\)^2} \(E-E^g\)\ \ \forall \in
\[E^{g+1/2},E^{g-1/2}\]\\
&\lim_{E\underset{>}{\to}E^{g+1/2}} E = E^{g+1/2,+}\\
&\lim_{E\underset{>}{\to}E^{g-1/2}} E = E^{g-1/2,+}\\
& K \textrm{ is a cell}
\end{align}  
Using this energy discretization and upwind in energy, (\ref{b-csd}) becomes :
\begin{equation}
\begin{split}
&\Delta E^g \oint_{\pk} \(\bo \cdot \bs{n}\) \Psi_{\br}^{g} \(b_{\br}^g(\br,E^g) 
\cdot b_{\br}^{g,T}(\br,E^g)\) ds - \Delta E^g \int_K \(\Psi_{\br}^{g,T} \cdot 
b_{\br}^g\(\br,E^g\)\) \(\bo_d \cdot \bn b_{\br}^{g}\(\br,E^g\)\) d\br\\
&+ \Delta E^g \int_K \Sigma_t^g\(\br\) \Psi_{\br}^{g}\(b_{\br}^{g}(\br,E^g)\cdot 
b_{\br}^{g,T}\(\br,E^g\)\) d\br = \int_k \sum_{g'=1}^G \sum_{l=0}^L \sum_{m=-l}^l 
\Delta E^{g'} \frac{2l+1}{4\pi} \Sigma_{s,l}^{g'\rightarrow g}(\br)\\
&\Phi_{l}^{m,g'} Y_m^l\(\bo_d\)\(b_{\br}^{g',T}(r,E^{g'})\cdot b_{\br}^g\(\br,E^g\)\) 
d\br + \int_{K} d\br \(S^{g-1}(\br)\(\Psi^{g-1,T}\cdot b^{g-1}\(\br,E^{g-1/2,+}\)\)
\right.\\
& - S^{g}(\br) \left. \(\Psi^{g,T}\cdot b^g\(\br,E^{g+1/2,+}\)\)\) b_{\br}^g
(\br,E^g)
\end{split}                                   
\end{equation}          
\begin{equation}
\begin{split}
&\frac{\Psi_E^g}{3\Delta E^g} \int_K \Sigma_t(d\br) d\br =
\sum_{l=0}^L \frac{2l+1}{4\pi} \sum_{m=l}^l \frac{\Phi_l^{m,g}
Y_l^m\(\bo_d\)}{3} \int_K \Sigma_{s,l}^{g' \rightarrow g}\(\br\) d\br \\
&\int_K \frac{S^{g-1}(\br)}{\Delta E^g} \(\Psi_d^{g-1,T}(\br) \cdot
b^{g-1}(\br,E^{g-1/2})\) d\br - \int_K \frac{S^g}{\Delta E^g} \(\Psi_d^{g,T}
\cdot b_{\br}^g (\br,E^{g+1/2}) +\Psi_E^g\) 
\end{split}
\end{equation}   
The second part is to implement an efficient preconditioner. The most 
common method to accelerate the convergence of the transport equation is to use 
a P1 Synthetic Acceleration scheme (P1SA) or a Diffusion Acceleration scheme 
(DSA) \cite{adams}. Next we present the P1SA equation but first let us write the primal and the adjoint angular fluxes as :
\begin{align}
& \Psi_m = \frac{1}{4 \pi} \left(\Phi + 3 \boldsymbol{J}\cdot
\boldsymbol{\Omega}_m\right) \label{eq1}\\
& \Psi_m^* = \frac{1}{4 \pi} \left(\Phi + 3 \boldsymbol{J}^*\cdot
\boldsymbol{\Omega}_m\right) \label{eq2}
\end{align}
The $S_N$ variational form of the transport equation for neutral particle is given 
by (see also \cite{jcam}) :
\begin{equation}
b(\Psi,\Psi^*) - \sum_{e\in\partial \mathcal{D}^r} \sum_{\boldsymbol{\Omega}_m \cdot \boldsymbol{n}_b < 0} w_m \left\langle\Psi_{m'},\Psi_m^*\right\rangle_e - \sum_{n=0}^N \sum_{k=-n}^n \frac{2n+1}{4\pi} \left(\Sigma_{s,n}\Phi_{n,k},\Phi_{n,k}^*\right)_{\mathcal{D}} = l(\Psi^*)
\end{equation}
where the bilinear and the linear forms are :
\begin{equation}
\begin{split}
b(\Psi,\Psi^*) &= \sum_{d=1}^M w_m \left(\left(\boldsymbol{\Omega}_m \cdot \boldsymbol{\nabla}+\Sigma_t\right)\Psi_d,\Psi_d^*\right)_{\mathcal{D}} + \sum_{d=1}^M \left\langle\llbracket\Psi_d\rrbracket,\Psi_d^{*+}\right\rangle_{E_h^i}\\
&+\sum_{e\in\partial \mathcal{D}} \sum_{\boldsymbol{\Omega}_d \cdot \boldsymbol{n}_b < 0} w_d \left\langle\Psi_d,\Psi_d^*\right\rangle_e
\end{split}
\end{equation}
\begin{equation}
l(\Psi^*) = \sum_{l=0}^L \sum_{m=-l}^l
\left(Q_{l,m},\Phi_{l,m}^*\right)_{\mathcal{D}} + \sum_{e\in\partial
\mathcal{D}^d} \sum_{\bo_d \cdot \boldsymbol{n}_b} w_d
\left\langle\Psi_d^{inc},\Psi_d^*\right\rangle_e
\end{equation}
where :
\begin{itemize}
\item $\mathcal{D}$  is the domain. 
\item $\partial\mathcal{D}$ is the boundary of the domain.
\item $\partial\mathcal{D}^r$ is the reflective boundary of the domain.
\item $\partial\mathcal{D}^d$ is the Dirichlet boundary of the domain.
\item $\boldsymbol{n}_b$ is the normal vector on the domain boundary.
\item $\Psi_d^{\pm} = \lim_{s\to 0^{\pm}} \Psi_d (\boldsymbol{r} + s \boldsymbol{\Omega}_d)$
\item $\llbracket\Psi_d\rrbracket = \Psi_d^+ - \Psi_d^-$ is the inter element jump.
\item $E_h^i$ is the set of all interior edges.
\item $(f,g)_{\mathcal{D}} = \sum_{K \in \mathcal{T}} (f,g)_K$ with  $(f,g)_K = \int_K f\ g\ d\mathbf{r}$
\item $\left\langle f,g\right\rangle_{\mathcal{D}} = \sum_{e \in \mathcal{E}_h^i} \left\langle f,g\right\rangle_e$ with  $\left\langle f,g\right\rangle_e = \int_e \left| \boldsymbol{\Omega}_m \cdot \boldsymbol{n}(\mathbf{r})\right| ds$
\item $Q_{l,m}$ are the moments volumetric source (scattering and fixed external source).
\end{itemize}
Using (\ref{eq1}) and (\ref{eq2}) in the bilinear and  linear form, we find
after some algebra :
\begin{equation}
b\left(\Phi,\boldsymbol{J},\Phi^*,\boldsymbol{J}^*\right) = l\left(\Phi^*,\boldsymbol{J}^*\right)
\label{P1SA}
\end{equation}
with :
\begin{equation}
\begin{split}
b(\Phi,\boldsymbol{J},\Phi^*,\boldsymbol{J}^*) &= \left(\Sigma_a \Phi,\Phi^*\right)_D + \left(3\Sigma_{tr} \boldsymbol{J},\boldsymbol{J}^*\right)_D+\left(\boldsymbol{\nabla} \Phi,\boldsymbol{J}^*\right)_D - \left(\boldsymbol{J},\boldsymbol{\nabla} \Phi^*\right)_D\\
&+ \frac{1}{4} \left(\llbracket\Phi\rrbracket,\llbracket\Phi^*\rrbracket\right)_{E_h^i}+\left(\llbracket\Phi\rrbracket,\ldb\boldsymbol{J}^*\rdb\cdot\boldsymbol{n}\right)_{E_h^i} -
\left(\ldb\boldsymbol{J}\cdot\boldsymbol{n}\rdb,\llbracket\Phi^*\rrbracket\right)_{E_h^i}\\
& + \frac{9}{16}\left(\llbracket \boldsymbol{J}\cdot\boldsymbol{n}\rrbracket,\llbracket \boldsymbol{J}^*\cdot\boldsymbol{n}\rrbracket\right)_{E_h^i} + \frac{9}{16}\left(\llbracket\boldsymbol{J}\rrbracket, \llbracket \boldsymbol{J}^*\rrbracket\right)_{E_h^i}\\
&+\frac{1}{4}\left(\Phi,\Phi^*\right)_{\partial D^d} + \frac{1}{2} \left(\Phi,\boldsymbol{J}\cdot \boldsymbol{n}\right)_{\partial D^d} - \frac{1}{2}\left(\boldsymbol{J}\cdot\boldsymbol{n},\Phi^*\right)_{\partial D^d}\\
&+\frac{9}{16}\left(\boldsymbol{J},\boldsymbol{J}^*\right)_{\partial D^d} + \frac{9}{16}\left(\boldsymbol{J}\cdot\boldsymbol{n},\boldsymbol{J}^*\cdot\boldsymbol{n}\right)_{\partial D^d}+\frac{9}{4} \left(\boldsymbol{J}\cdot\boldsymbol{n}, \boldsymbol{J}\cdot\boldsymbol{n}\right)_{\partial D^r}
\end{split}
\end{equation}
and :
\begin{equation}
l(\Phi^*,\boldsymbol{J}^*) = \left(Q_0,\Phi^*\right)_D + \left(3\boldsymbol{Q}_1,\boldsymbol{J}^*\right)_D + \left(J^{inc},\Phi^*\right)_{\partial D^d} - \left(\boldsymbol{\Upsilon}^{inc},\boldsymbol{J}^*\right)_{\partial D^d}
\end{equation}
where $Q_0$ is the zeroth moment of the source, $\boldsymbol{Q}_1$ is the first moment of the source :
\begin{equation}
J^{inc} = -\sum_{\boldsymbol{\Omega}_d \cdot \boldsymbol{n}(\boldsymbol{r}_b)<0} w_d |\boldsymbol{\Omega}_d \cdot \boldsymbol{n}\left(\boldsymbol{r}_b)\right)| \Psi_d^{inc}
\end{equation}
$\Phi^d$ is the flux on the Dirichlet boundary and :
\begin{equation}
\boldsymbol{\Upsilon} = - \sum_{\boldsymbol{\Omega}_d \cdot \boldsymbol{n}(\boldsymbol{r}_b)<0} 3w_d\boldsymbol{\Omega}_d |\boldsymbol{\Omega}_d \cdot \boldsymbol{n}\left(\boldsymbol{r}_b)\right)| \Psi_d^{inc}
\end{equation}
The problem with the P1SA or the DSA methods is that they are not stable when the 
anisotropy is too large. The acceleration scheme that we presented converges for 
any anisotropy when the medium is thick but not when
the cells are thin. Since in (\ref{b-csd}) we approximate the 
forward-peaked scattering of the electrons by a Dirac distribution, the 
anisotropy is very large. Thus, we will have to modify the acceleration scheme 
used. We already studied some 
properties of this scheme when the updating method is modified \cite{russe} and 
when the number of sweeps, which use the acceleration scheme, has been modified
\cite{multisweep}. The results were encouraging but they have to be confirmed for
electron transport which is much more anisotropic that what we have tried. If
the acceleration scheme remains instable while using the previous methods,
generalisation of the Modified $P_N$ Synthetic Acceleration or the Modified
DSA \cite{kassem} will be used.\\
The last interesting algorithm is the algorithm to compute the uncollided flux 
in parallel. The standard algorithms to compute the uncollided flux are not 
scalable. They either require to have the whole mesh in memory or the processors 
close to the source do most of the work.\\ 
The first collision source can be easily expressed mathematically by rewriting 
(\ref{b-csd}) using operator notation :
\begin{align}
&L \Psi = H \Phi + Q\\
&\Psi = \Psi^{inc}
\end{align}

\begin{align}
&L \(\Psi^u + \Psi^c\) = H \(\Phi^u + \Phi^c\) + Q\\
&\Psi^u + \Psi^c = \Psi^{inc}
\end{align}
That we can rewrite :
\begin{align}
& L\Psi^u = 0\\
& \Psi^u = \Psi^{inc}
\end{align}

\begin{align}
& L\Psi^c = H \Phi^u + H\Phi^c + Q \label{last}\\
& \Psi^c = 0
\end{align}

If we have several groups, we can rewrite (\ref{last}) :
\begin{equation}
L \Psi^{c,g} = H \Phi^{c,g} + H \Phi ^{u,g} + \sum_{g'\neq g}H\Phi^{g'}+Q
\end{equation}

% Optimization part
\input{optimization}
